
# Platforms 

We had several questions in the survey to talk about the attributes of the platform that folks wanted. 

## Platform Options

We asked people to tell us "Which of the following platforms would you most like to see the XOXO community migrate to?" Several options were pre-populated based on what had been suggested already in the Slack. 

Below is a chart sharing the results: 

```{r platform-barchart, echo=FALSE, message = FALSE, fig.height=6, fig.width=8}
# Platform Data 

library(googlesheets4)
library(tidyverse)
library(janitor)

gs4_auth()

k <- read_sheet("https://docs.google.com/spreadsheets/d/1jPKow4_vQ8CMUBfIYf_SyXNC-6hJNsg1AP0zcS-pOiY/edit?gid=386609990#gid=386609990", sheet = "PlatformCodes")

k_plat <- k %>% 
  select(Timestamp, Code) %>% 
  filter(!is.na(Code)) %>%  # Remove rows where 'Code' is NA
  separate_rows(Code, sep = ", ") %>% 
  mutate(Code = case_when(
    Code == "NoOpinion" ~ "No opinion on platform",
    Code == "NotFam" ~ "Not familiar with options",
    Code == "WillGo" ~ "Will go where group goes",
    Code == "SelfHost" ~ "Any platform that is self hosted", 
    Code == "DontLike" ~ "Dislike options", 
    TRUE ~ Code
  )) %>% 
  arrange(Code) %>% 
  count(Code, sort = TRUE) %>% 
  arrange(desc(n))

ggplot(k_plat, aes(x = fct_reorder(Code, n), y = n)) +
  geom_bar(stat = "identity", fill = "blue") +  # Set the fill color to blue
  geom_text(aes(label = n), 
            hjust = -0.2,  # Adjust horizontal position of labels
            size = 3) +     # Set the text size
  coord_flip() +
  labs(
    title = "Platform Preferences Counts",
    x = "Platform",
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 8),
    plot.margin = margin(t = 20, r = 20, b = 20, l = 20)  # Adjust margins: top, right, bottom, left
  )




```


The favorite was Discord, followed closely by Slack and then Discourse. The question was multiple select, so folks voted for as many as they wanted and there is overlap in what people responded with. 

Some folks wrote in to say that they didn't know the differences between the platforms, that they didn't have an opinion and that they would follow where the group would go. 


## Computer vs. Mobile

Survey designers were curious to know how important mobile vs. computer usage would be for the platform. We can see clearly from the chart that most people use both, and so functionality on both mobile and computers is important. 

```{r platform-piechart, echo=FALSE, message = FALSE, fig.height=6, fig.width=8}

library(RColorBrewer)

j<- read_sheet("https://docs.google.com/spreadsheets/d/1yeSmBHVX16hciEBfPRj376aNrC_UCvbY2gxbzBp1uzU/edit?resourcekey=&gid=1115108170#gid=1115108170")

j_clean <- j %>% 
  clean_names() %>% 
  rename_with(~paste0("Q", seq_along(.)))

j_cleaner <- j_clean %>% 
  rename(
    Timestamp = Q1,
    Values = Q2, 
    Appreciate = Q3,  
    Concerns = Q4, 
    Platform = Q5, 
    CompMobile = Q6, 
    OppPlat = Q7, 
    ConcernPlat = Q8, 
    Name = Q9, 
    Impact = Q10, 
    Andys = Q11, 
    Else = Q12
  )

j_dat <- j_cleaner %>%
  select(Timestamp, CompMobile)

comp_counts <- j_dat %>%
  filter(!is.na(CompMobile)) %>%
  count(CompMobile) %>%
  mutate(percentage = n / sum(n) * 100)  # Calculate percentages

# Define a colorblind-friendly palette using RColorBrewer
color_palette <- brewer.pal(n = 3, name = "Blues")


ggplot(comp_counts, aes(x = "", y = n, fill = CompMobile)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), 
            position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values = color_palette) +  # Apply the colorblind-friendly palette
  labs(
    title = "Distribution of Device Usage Preferences",
    fill = "Device Usage"
  ) +
  theme_void() +  # Remove axes and background
  theme(
    legend.position = "right",
    plot.margin = margin(t = 30, r = 30, b = 30, l = 30)  # Add padding: top, right, bottom, left
  )


```

